Formalization of Typed Lua

### 2015-06-10 doc/papers/paper/paper.tex
Fixing the statistics about list iteration

The rest of the paper is organized as follows:
Section \ref{sec:statistics} presents the methodology and results of
our survey of Lua idioms;
Section \ref{sec:types} presents the types of Typed Lua's
type system, and their subtyping and consistent-subtyping relations;
Section \ref{sec:tables} presents the typing rules for evolution of table types;
Section \ref{sec:projections} presents the typing rules for
destructuring unions of tuples into projection types and
flow typing on these projections;
Section \ref{sec:related} reviews related work;
Section \ref{sec:conclusion} presents our conclusions,
and outlines our plans for future work.

@@

In order to gauge how frequently tables are used as
collections, we looked for the presence of code that
iterates over tables, and found out that 23\% of the
scripts in our corpus iterate over a map at least once,
and 31\% of the scripts iterate over a list
at least once. \emph{TODO: Não sei se esse número está correto,
apenas somei as duas porcentagens, mas pode haver interseção.}

>>>>

The rest of the paper is organized as follows:
Section \ref{sec:statistics} presents the methodology and results of
our survey of Lua idioms;
Section \ref{sec:types} presents the types of Typed Lua's
type system, and their subtyping and consistent-subtyping relations;
Section \ref{sec:rules} presents the typing rules for evolution of table types,
and the typing rules for destructuring unions of tuples into projection types,
allowing flow typing on these projections;
Section \ref{sec:related} reviews related work;
Section \ref{sec:conclusion} presents our conclusions,
and outlines our plans for future work.

@@

In order to gauge how frequently tables are used as
collections, we looked for the presence of code that
iterates over tables, and found out that 23\% of the
scripts in our corpus iterate over a map at least once,
and 27\% of the scripts iterate over a list at least once.
